EinsteinPy: Python for General Relativity\footnote{Released on July, 15th, 2019}

### 2020-01-02 paper.tex
symbolic edits

%# calculates the trajectory
%ans = obj.calculate_trajectory(
    %end_lambda=end_lambda, OdeMethodKwargs={"stepsize": stepsize}, return_cartesian=True
%)
%\end{minted}
\subsection{plotting}
\subsection{symbolic}
\subsection{hypersurface}
This module provides with basic computational functions which are essential for modelling the space-like hypersurface for any spacetime geometry. Currently module has implementation for Schwarzschild geometry with conversion functions from Schwarzschild coordinates to 3-D spherical coordinates and some plotting utilities. The whole module is expected to extend for providing a superclass for implementations related to gravitationl lensing simulations and numerical calculations of null geodesics on hypersurfaces and deviation angles for systems which are relevant to relativistic astrophysical problems. A small code snippet for plotting the hypersurface is as follows:
%\begin{minted}[linenos]{python}
%# importing the modules
from einsteinpy.hypersurface import SchwarzschildEmbedding
from astropy import units as u

>>>>

%# calculates the trajectory
%ans = obj.calculate_trajectory(
    %end_lambda=end_lambda, OdeMethodKwargs={"stepsize": stepsize}, return_cartesian=True
%)
%\end{minted}
\subsection{plotting}
\subsection{symbolic}
General Relativity required heavy mathematical formulation to derive and describe various tensors attributing to various features essential for cogent description of a arbitrary space-time. We would describe the various quantities currently supported by this module while maintaining brevity. 
\subsection{hypersurface}
This module provides with basic computational functions which are essential for modelling the space-like hypersurface for any spacetime geometry. Currently module has implementation for Schwarzschild geometry with conversion functions from Schwarzschild coordinates to 3-D spherical coordinates and some plotting utilities. The whole module is expected to extend for providing a superclass for implementations related to gravitationl lensing simulations and numerical calculations of null geodesics on hypersurfaces and deviation angles for systems which are relevant to relativistic astrophysical problems. A small code snippet for plotting the hypersurface is as follows:
%\begin{minted}[linenos]{python}
%# importing the modules
from einsteinpy.hypersurface import SchwarzschildEmbedding
from astropy import units as u
